
\documentclass[]{deedy-resume-openfont}


\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     LAST UPDATED DATE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\lastupdated

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     TITLE NAME
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\namesection{Nabarun}{Chatterjee}{
\href{mailto:nabarun.chatterjee@gmail.com}{nabarun.chatterjee@gmail.com} | +(91) 819-777-2826
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN ONE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{minipage}[t]{0.33\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Education} 

\subsection{Kalyani Government}
\subsection{Engineering College}
\descript{MTech in Computer Science}
\location{2011 - 2013 | Kalyani, WB}
\sectionsep

\subsection{Ramakrishna Mission}
\subsection{Vivekananda University}
\descript{M.Sc in Computer Science}
\location{2009-2011 | Belur, WB}
\sectionsep

\subsection{Ramakrishna Mission}
\subsection{Vidyamandira}
\descript{B.Sc in Computer Applications}
\location{2006-2009 | Belur, WB}
\sectionsep

\subsection{Don Bosco School}
\location{ISC(10+2) 2005|  Bandel, WB}
\location{ICSE(10) 2003|  Bandel, WB}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     LINKS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Links}
Github:// \href{https://github.com/nabarunchatterjee}{\custombold{nabarunchatterjee}} \\
\sectionsep
LinkedIn://  \href{https://www.linkedin.com/in/nabarunchatterjee}{\custombold{nabarunchatterjee}} \\
\sectionsep


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SKILLS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Skills}
\subsection{Programming}
Python \textbullet{}   Shell \textbullet{} Golang(Beginner) \\
\textbullet{} \LaTeX\ \\
\sectionsep
\subsection{Tools}
Terraform \textbullet{} Packer \textbullet{} Vagrant \textbullet{} Ansible \\
\textbullet{} Saltstack  \textbullet{} Chef \textbullet{} Mesos Marathon\\
\sectionsep
\subsection{Cloud}
AWS \textbullet{} Microsoft Azure\\
\sectionsep
\subsection{Others}
Flask \textbullet{} Wireshark \textbullet{} MySQL
\sectionsep

\section{Want to Learn}
\subsection{Technology}
Kubernetes  \textbullet{} Cryptography  \textbullet{} AI
 \textbullet{} Computational Geometry
\sectionsep
\subsection{Others}
Photography  \textbullet{} Spanish Language


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN TWO
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{minipage}
\hfill
\begin{minipage}[t]{0.66\textwidth}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Experience}

\runsubsection{Olacabs}
    \descript{| Production Engineer (Core Infrastructure) }
\location{June 2016 – Present | Bengaluru}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}
\item Rest Apis over Terraform and Packer in Python for creating infrastructure in AWS and Azure.
\item Create linux users and groups and manage permissions for all machines accross the stack.
\item Setup migration from chef 11 to chef 12 and automate creation of cookbook source dynamically using Berkshelf and gitlab webhooks.
\item Expose Rest Apis to automate CRUD for RRsets.
\end{tightemize}
\sectionsep

\runsubsection{Knowlarity}
\descript{| Devops Engineer }
\location{April 2015 – May 2016 | Bengaluru}
\begin{tightemize}
\item Automating Telephony Cluster Creation(Ansible)
\item Automating Phasewise Release of Telephony Platform(Ansible)
\item Monitoring Events and Inventory(Salt)
\end{tightemize}
\sectionsep

\runsubsection{Plivo}
\descript{| Devops Engineer }
\location{June 2013 – Dec 2013 and Aug 2014 - May 2014| Bengaluru}
\begin{tightemize}
\item Call Quality Analyzer - Extraction of all call detail records, audio, disconnection quality parameters like latency, jitter, ptime and detecting probable issues if extracted values are outside a predefined range.
\item Automation of the Process of Number Testing, Improvement of  chat bot and tools for internal analytics
\item Handling and debugging service and server monitoring alerts. Debugging customer facing call quality issues.
\end{tightemize}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     RESEARCH
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Research}
\runsubsection{Kalyani Goverment Engineering College}
\descript{| MTech Project}
\location{2012 – 2013  | Kalyani, WB}
    \custombold{Detection of Blackhole Behaviour Using Triangular Encryption in NS2} \href{http://www.sciencedirect.com/science/article/pii/S2212017313005537}{[Paper Link]}
\sectionsep
\sectionsep

\runsubsection{Indian Statistical Institute}
\descript{| Project Linked Person }
\location{Feb 2014 – July 2013  | Kolkata, WB}
    \custombold{Nature Inspired Heuristics for Large Scale Dynamic Engineering Problems} \href{https://github.com/nabarunchatterjee/EvoComp}{[Github Link]}
\sectionsep
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Projects
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Projects}
\runsubsection{Ramakrishna Mission Vivekananda University}
\descript{| M.Sc. Project}
\location{2010 – 2011 | Belur, WB}
    \custombold{A Hybrid Minimum Spanning Tree Algorithm on the GPU} - A mixture of the Prim's and the Boruvka's approach to find the minimum spanning tree of a graph. The implementation uses Nvidia's GPUs and CUDA and scalable primitives like scan, segmented scan, compact and split to perform the task.
\sectionsep
\sectionsep

\runsubsection{Ramakrishna Mission Vidyamandira}
\descript{| B.Sc. Project }
\location{Feb 2008 – July 2009  | Kolkata, WB}
    \custombold{Implementation of the RSA Algorithm}
\sectionsep
\sectionsep


\end{minipage}
\end{document}  \documentclass[]{article}
